Minimizing post-shock forecasting error using disparate information

### 2020-06-16 manuscript/manuscript.tex
revision to sim.study.R and manuscript

Proposition \ref{uniqueness} details some conditions when $\mathbf{W}^*$ is unique.  Note that $\mathbf{V}$ is $2p \times n$. Therefore, if the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $2p \geq n$. However, when $2p < n$, $\mathbf{W}^*$ may not be unique.

@@

\subsubsection{Under $\mc{M}_{21}$ and $\mc{M}_{22}$}

According to Proposition \ref{propriskwadj2} and the discussion in Section \ref{conditionsm2122}, the risk-reduction quantities $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
\begin{align*}
  \Delta_{\rm adj} 
  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2
\quad   \text{ and } \quad 
  \Delta_{\rm wadj} 
  = (\E{\alpha_1})^2-\var{\hat{\alpha}_{\rm wadj}}.
\end{align*}
In this case, the risk-reduction quantity for $\hat{\alpha}_{\rm adj}$ is similar to that of $\hat{\alpha}_{\rm IVW}$ since they are both biased for $\E{\alpha_1}$.  Thus,
\begin{align*}
 \Delta_{\rm IVW} 
  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2
\end{align*}

@@

%In particular $\overline{\hat{\alpha}_{\rm wadj}}$ will provide an approximation for $\E{\alpha_1}$ under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ since it is unbiased for $\E{\alpha_1}$ under those three configurations from Proposition \ref{unbiased}. Therefore, we can judge whether to use a shock-effect estimator, and choose between shock-effect estimators by this method.

@@

@@

Parameter setup of our simulations are detailed as below. $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$. We  sampled $T_i$'s  independently from  $\Gamma(15, 10)$ that are further rounded to integers. If it exists some  $i$ such that  $T_i < 90$, we let $T_i=90$ instead.  It is set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. Moreover, it is also designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. However, it is still possible that the design matrix for the bootstrapped model does not have full rank for some $b\in \{1, \ldots, B\}$. In that case, we do not consider such $b$ in computations of means and variances. Additionally, we generated the covariates from $\Gamma(1,10)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.

In this experiment, we consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\gamma}$ and $\sigma_{\delta}$ in the model $\delta_i \sim \normal{2\mathbf{1}_p}{\sigma^2_{\delta}\mathbf{I}_p}$, and $\gamma_i \sim \normal{2\mathbf{1}_p}{\sigma^2_{\gamma}\mathbf{I}_p}$. We used 200 replications of Monte Carlo simulations and $B = 500$ for computation; and report means and standard errors for estimated quantities accordingly.

@@

In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\gamma}= \sigma_{\delta}=\sigma_{\alpha} \in  \{0.01, 0.1, 1, 10\}$ where we fix $\sigma$ to 1. The bias results are not reported for $\hat{\alpha}_{\rm IVW}$ since its moments are generally unknown. It is shown in Table ? that as the donor pool size increases, the bias and consistency results improve with more precision. In contrast, the result gets poorer as  the variance of $\alpha_i$ increases. It is to be expected since the consistency results claimed in Section \ref{varbootstrap} are conditioned on $\Theta$. Under a fixed design, it is evident that the results of our risk-reduction propositions are highly consistent if the models for $\alpha_i$'s  are identified correctly with appropriate covariates. But it is reversed in the random design case. Moreover, notice that the consistency for voting the best estimator works poor when $n$ is small but improves significantly when $n$ is large.

@@

Our bootstrap procedures can be extended to approximate the distribution of shock effect estimators from more general time series. The pseudo time series generated by parametric bootstrap is not stationary. Note that \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$. This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$ where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$; for $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$. The sampling stops when $N$ observations are reached. Note that the collection of random positions $\{I_n \colon n \in \mathbb{N}\}$ is a sequence of i.i.d. discrete uniform random variables; and the collection of random lengths $\{L_n \colon n \in \mathbb{N}\}$ is a sequence of  i.i.d. geometric random variables with parameter $p$.  However, the consistency needs to be proved by a case-by-case analysis \citep[Page 66]{politis1999subsampling}. Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$. This issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.  More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, and \citet{berkowitz2000recent}. It is up to  users in terms of selecting which procedure to choose but under different assumptions on the time series.

In terms of the use of our bootstrap procedure, we caution that the bootstrapping residuals in OLS estimation may not provide valid inference in high dimension where $p < T_i$ but $p / T_i$ is not close to zero for $i\in \{2, \ldots, n+1\}$ \citep{el2018can}. Recall that in Section \ref{varbootstrap}, we proposed two possible bootstrap procedures, $\mc{B}_u$  and $\mc{B}_c$. There are some philosophical distinctions between $\mc{B}_u$  and $\mc{B}_c$. $\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors. In contrast $\mc{B}_c$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error. Therefore, it is possible that $\mc{B}_u$ can improve precision of $\mc{B}_2$. In this study, for the use of $\mc{B}_u$, we assume $\mathbf{W}^*$ is non-degenerate in the population with taking zero weight. However, it is likely that $\mathbf{W}^*$ may possibly take values on the boundary of $\mc{W}$, in which case $\mc{B}_u$ may fail for $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}. For example, $w_i^*=0$ for some $i \in \{2, \ldots, n+1\}$. In this regard, the subsampling in Section 4 of \citet{li2019statistical} may adapt to our scenario to solve this problem by resampling $m$ candidates from donor pool with the conditions $m \to \infty$, and $m/n \to 0$ as $n \to \infty$. But we may leave its mathematical justification for future research. Note that this problem will not occur under  $\mc{B}_c$ because  if $w_i^*=0$ for some $i$, $w_i^*=0$ makes it impossible for bootstrap estimate of $\hat{\alpha}_i$ to contribute to the bootstrap estimate of distribution of $\hat{\alpha}_{\mrm{wadj}}$. That being said, if in practice users detect the boundary case (e.g., $\mathbf{W}^*$ in Section \ref{forecasting}), they are not recommended to use $\mc{B}_u$. Besides, we  recommend using $\mc{B}_c$ when the donor pool size $n$ is small. When $n$ is large, the selection would be more up to how users think of the philosophical differences between $\mc{B}_u$ and $\mc{B}_c$ up to application of interest, and the problems that  $\mc{B}_u$ may fail.

For the use of our methodology, caution should be dedicated to the construction of donor pool. If the donor pool includes some individuals that are not similar to the time series of interest, the result will possibly not be robust to the introduced noises.   Additionally, according to Section \ref{parametricbootstrapsimulation}, we recommend using estimated risk-reduction quantities for voting best shock-effect estimator only when $n$ is large. It is  due to the fact that plug-in estimation of  risk-reduction quantities gains more precision when $n$ becomes large.

>>>>

Proposition \ref{uniqueness} details some conditions when $\mathbf{W}^*$ is unique.  Note that $\mathbf{V}$ is $2p \times n$. Therefore, if the covariates are of full rank and the true solution lies in the convex and compact $\mathcal{W}$, a sufficient condition for $\mathbf{W}^*$ to be unique is $2p \geq n$. However, when $2p < n$, $\mathbf{W}^*$ may not be unique. If it exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $2p < n$, there are infinitely many solutions to (\ref{SCM}).  The issue of non-uniqueness is further discussed in Section \ref{discussion}.

@@

\subsubsection{Under $\mc{M}_{21}$ and $\mc{M}_{22}$}
\label{section322}
According to Proposition \ref{propriskwadj2} and the discussion in Section \ref{conditionsm2122}, the risk-reduction quantities $\hat{\alpha}_{\rm adj}$ and $\hat{\alpha}_{\rm wadj}$ are
\begin{align*}
  \Delta_{\rm adj} 
  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2
\quad   \text{ and } \quad 
  \Delta_{\rm wadj} 
  = (\E{\alpha_1})^2-\var{\hat{\alpha}_{\rm wadj}}.
\end{align*}
In this case, the risk-reduction quantity for $\hat{\alpha}_{\rm adj}$ is similar to that of $\hat{\alpha}_{\rm IVW}$ since they are both biased for $\E{\alpha_1}$.  Thus,
\begin{align*}
 \Delta_{\rm IVW} 
  = (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm IVW}} -(\E{\hat{\alpha}_{\rm IVW}}-\E{\alpha_1})^2
\end{align*}

@@

@@

In particular, $\overline{\hat{\alpha}_{\rm wadj}}$ will provide an approximation for $\E{\alpha_1}$ under $\mc{M}_1$, $\mc{M}_{21}$, and $\mc{M}_{22}$ since it is unbiased for $\E{\alpha_1}$ under those three configurations from Proposition \ref{unbiased}. Therefore, we can estimate the risk-reduction quantities in Section \ref{comparisons} using the estimates from the parametric bootstrap. For example, the $\Delta_{\rm adj}$ and its estimator $\hat{\Delta}_{\rm adj}$ are
\begin{align*}
  \Delta_{\rm adj} 
  &= (\E{\alpha_1})^2 -\var{\hat{\alpha}_{\rm adj}} -(\E{\hat{\alpha}_{\rm adj}}-\E{\alpha_1})^2 \\
  \hat{\Delta}_{\rm adj} 
 & = (\overline{\hat{\alpha}_{\rm wadj}})^2 -S^2_{\hat{\alpha}_{\rm adj}} -(\overline{\hat{\alpha}_{\rm adj}}-\overline{\hat{\alpha}_{\rm wadj}})^2,
\end{align*}
where $S^2_{\hat{\alpha}_{\rm adj}}$ is the bootstrap sample variance for $\hat{\alpha}_{\rm adj}$. Suppose the $\hat{\Delta}_{\rm wadj}$ and $\hat{\Delta}_{\rm IVW}$ are estimators for $\Delta_{\rm wadj}$ and $\Delta_{\rm IVW}$, respectively. Then, we can evaluate the risk-reduction propositions by judging whether $\hat{\Delta}_{\rm est}>0$ for $\text{est} \in \{\text{adj}, \text{wadj}, \text{IVW}\}$, and  the best estimator $\hat{\alpha}_{\rm best}$ is the one with the maximum estimated risk-reduction quantities.

@@

Parameter setup of our simulations are detailed as below. $\phi_i$'s are sampled independently from $\mrm{Uniform}(0,1)$. We  sampled $T_i$'s  independently from  $\Gamma(15, 10)$ that are further rounded to integers. If it exists some  $i$ such that  $T_i < 90$, we let $T_i=90$ instead.  Moreover, $T_i^*$ is randomly selected from $2p + 4$ to $T_i-1$. Those are set up to satisfy a necessary condition for the design matrix of OLS estimation to have full rank. Moreover, it is also designed to illustrate the performance of $\hat{\alpha}_{\rm IVW}$ that may perform well in time series with varying lengths. However, it is still possible that the design matrix for the bootstrapped model does not have full rank for some $b\in \{1, \ldots, B\}$. In that case, we do not consider such $b$ in computations of means and variances. Additionally, we generated the covariates from $\Gamma(1,10)$ to set up a setting when the $\hat{\alpha}_{\rm wadj}$ may perform well.

In this experiment, we consider parameter setup by varying $\sigma$ in the model of $y_{i,t}$, $n$, the donor pool size, and $\sigma_{\alpha}$ in the model of $\alpha_i$. We used 200 replications of Monte Carlo simulations and $B = 500$ for computation; and report means and standard errors for estimated quantities accordingly.

@@

In the first experiment, we consider the parameter combination of  $n \in \{5, 10, 15, 25\}$ and $\sigma_{\alpha} \in  \{1, 5, 10, 25, 100\}$ where we fix $\sigma$ to 1. The bias results are not reported for $\hat{\alpha}_{\rm IVW}$ since its moments are generally unknown. It is shown in Table ? that as the donor pool size increases, the bias and consistency results improve with more precision. In contrast, the result gets poorer as  the variance of $\alpha_i$ increases. It is to be expected since the consistency results claimed in Section \ref{varbootstrap} are conditioned on $\Theta$. Under a fixed design, it is evident that the results of our risk-reduction propositions are highly consistent if the models for $\alpha_i$'s  are identified correctly with appropriate covariates. But it is reversed in the random design case. Moreover, notice that the consistency for voting the best estimator works poor when $n$ is small but improves significantly when $n$ is large.

@@

Under the setup of our model, non-uniqueness of $\mathbf{W}^*$ would not be a problem. It is because all risk-reduction propositions and other properties established will still hold. However, non-uniqueness may not be desirable in other model setup. For example, consider the model where $\alpha_i$ is assumed to be not identically distributed, the size of  donor pool to be 2, and there are two solutions to (\ref{SCM}), say, $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$ with $\var{\alpha_2}\neq \var{\alpha_3}$. In this scenario, the procedure of trying to recover $\alpha_1$ will fail since the resulting $\alpha_1$ will be different with different variances for $\mathbf{W}^*_1=(1,0)$ and  $\mathbf{W}^*_2=(0,1)$. If the non-uniqueness is of concern, users may select the weight that optimizes some objective function. For instance, in the example just discussed, users may select the weight that minimizes the estimated variance of $\hat{\alpha}_{\rm wadj}$.

Our bootstrap procedures can be extended to approximate the distribution of shock effect estimators from more general time series. The pseudo time series generated by our proposed parametric bootstrap is not stationary. Note that \citet{politis1994stationary} motivated a stationary bootstrap method for strictly stationary and weakly dependent time series $\{X_n \colon n \in \mathbb{N}\}$. This algorithm generates a sequence of blocks of observations $B_{I_1, L_1}, B_{I_2, L_2}, \ldots$ where $B_{i,b}= \{X_i, X_{i+1}, \ldots, X_{i+b-1}\}$; for $j > N$, $X_{j}$ is defined to be $X_k$, where $k = j \hspace{-.1cm} \mod N$ and $X_0 = X_N$. The sampling stops when $N$ observations are reached. Note that the collection of random positions $\{I_n \colon n \in \mathbb{N}\}$ is a sequence of i.i.d. discrete uniform random variables; and the collection of random lengths $\{L_n \colon n \in \mathbb{N}\}$ is a sequence of  i.i.d. geometric random variables with parameter $p$.  However, the consistency needs to be proved by a case-by-case analysis \citep[Page 66]{politis1999subsampling}. Additionally, the asymptotic accuracy of this algorithm can be sensitive to the selection of $p$. This issue is similar to that of the selection of block size in moving-block bootstrapping \citep{kunsch1989jackknife, liu1992moving}.  More work related to bootstrapping time series  can be referred to Chapters 3 and 4 in \citet{politis1999subsampling}, and \citet{berkowitz2000recent}. It is up to  users in terms of selecting which procedure to choose but under different assumptions on the time series.

In terms of the use of our bootstrap procedure, we caution that the bootstrapping residuals in OLS estimation may not provide valid inference in high dimension where $p < T_i$ but $p / T_i$ is not close to zero for $i\in \{2, \ldots, n+1\}$ \citep{el2018can}. Recall that in Section \ref{varbootstrap}, we proposed two possible bootstrap procedures, $\mc{B}_u$  and $\mc{B}_c$. There are some philosophical distinctions between $\mc{B}_u$  and $\mc{B}_c$. $\mc{B}_u$ treats the donor pool as realizations from some infinite super-population of potential donors. In contrast $\mc{B}_c$ treats the donor pool as being fixed  and known before the analysis is conducted, where the randomness comes from parameters and idiosyncratic error. Therefore, it is possible that $\mc{B}_u$ can improve precision of $\mc{B}_2$.

In this study, for the use of $\mc{B}_u$, we assume $\mathbf{W}^*$ is non-degenerate in the population without taking zero weight.  Recall that in Section \ref{constructionofestimators} we note that if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM}) and $2p < n$, there will be infinitely many solutions to $\mathbf{W}^*$. In the simulation setup, we consider $2p >n$ such that the assumption can be reasonably satisfied. However, in the application, it is likely that $\mathbf{W}^*$ may  take values on the boundary of $\mc{W}$, in which case $\mc{B}_u$ may fail for $\hat{\alpha}_{\mrm{wadj}}$ \citep{andrews2000inconsistency}. In this regard, the subsampling in Section 4 of \citet{li2019statistical} may adapt to our scenario to solve this problem by resampling $m$ candidates from donor pool with the conditions $m \to \infty$, and $m/n \to 0$ as $n \to \infty$. But we may leave its mathematical justification for future research. Note that this problem will not occur under  $\mc{B}_c$ because  if $w_i^*=0$ for some $i$ and the weights are known, $w_i^*=0$ makes it impossible for bootstrap estimate of $\hat{\alpha}_i$ to contribute to the bootstrap estimate of distribution of $\hat{\alpha}_{\mrm{wadj}}$. Some recommendations for selection between  $\mc{B}_u$ and $\mc{B}_c$ are as below.

If in practice users detect the boundary case (e.g., $\mathbf{W}^*$ in Section \ref{forecasting}), they are not recommended to use $\mc{B}_u$. Moreover, if $2p < n$, $\mc{B}_u$ is also not recommended since the existence of infinitely many solutions is certain (if there exists some $\mathbf{W}^*$ satisfies (\ref{SCM})), and will guarantee degeneracy of  $\mathbf{W}^*$. Additionally, we  recommend using $\mc{B}_c$ when the donor pool size $n$ is small. When $n$ is large and $2p > n$, the selection would be more up to how users think of the philosophical differences between $\mc{B}_u$ and $\mc{B}_c$ up to application of interest, and the problems that  $\mc{B}_u$ may fail.

For the use of our methodology, caution should be dedicated to the construction of donor pool. If the donor pool includes some individuals that are not similar to the time series of interest, the result will possibly not be robust to the introduced noises.   Moreover, according to Section \ref{parametricbootstrapsimulation}, we recommend using estimated risk-reduction quantities for voting best shock-effect estimator only when $n$ is large. It is  due to the fact that plug-in estimation of  risk-reduction quantities gains more precision when $n$ becomes large.
